---
title: "Data and Research Question"
---

## Youth Risk Behavior Survey 2023

The Youth Risk Behavior Survey (YRBS) is a...

### Dataset Overview

-   **Source**: Centers for Disease Control and Prevention (CDC)
-   **Year**: 2023
-   **Target Population**: High school students
-   **Sample Size**: \[Add sample size\]

### Key Variables for the Research Question

The dataset includes information on various health-related behaviors:

1.  **Demographic Variables**
    -   ...
    -   ...
    -   ...
2.  **Outcome**
    -   ...
    -   ...
    -   ...
    -   ...
3.  **Predictors**
    -   ...
    -   ...
    -   ...
    -   ...

### Data Preprocessing

```{r}
#| label: data-prep

library(tidyverse)
library(dissertationData)
library(here)
data(clean_yrbs_2023)
# Add your data preprocessing code here
```

### Exploratory Data Analysis

```{r}
#| label: eda

```

### Creation of the Dataset

```{r}
#| label: create-dataset

# This is an example of how to create a dataset for a model.
# You can use this as a template to create your own dataset.


analysis_data <- clean_yrbs_2023 %>%
    select(Homelessness, NotGoodMentalHealth, GradesSchool, SocialMedia, Sex, Age, Race, ) |>
    filter(!is.na(NotGoodMentalHealth)) |>
    mutate(
        Homelessness = as.factor(Homelessness),
        NotGoodMentalHealth = as.factor(NotGoodMentalHealth),
        GradesSchool = as.factor(GradesSchool),
        SocialMedia = as.factor(SocialMedia),
        Sex = as.factor(Sex)
    )

# This is extremly important to save the dataset in the models folder!
# Without this, the model will not be able to find the dataset.

saveRDS(analysis_data, here::here("models", "data", "analysis_data.rds"))

```

### Splitting the Dataset

```{r}
#| label: split-dataset
#| include: false

set.seed(1990)

analysis_split <- initial_split(analysis_data,
    strata = NotGoodMentalHealth
)

analysis_train <- training(analysis_split)
analysis_test <- testing(analysis_split)

analysis_split

saveRDS(analysis_train, here::here("models", "data", "analysis_train.rds"))
saveRDS(analysis_test, here::here("models", "data", "analysis_test.rds"))

```

### Cross-Validation

```{r}
#| label: cross-validation
#| include: false

analysis_folds <- vfold_cv(analysis_train,
    v = 5
)
analysis_folds

saveRDS(analysis_folds, here::here("models", "data", "analysis_folds.rds"))
```